\documentclass[]{Keval-resume}
\usepackage{fancyhdr}
\usepackage{hyperref}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}

\hypersetup{%
 	colorlinks=false,% hyperlinks will be black
 	linkbordercolor=red,% hyperlink borders will be red
 	pdfborderstyle={/S/U/W 0.25}% border style will be underline of width 0.25pt
 }
 
\newlength\boxwid%  
\let\oldtextbullet=\textbullet
\def\textbullet{%
    \settowidth{\boxwid}{\indent\oldtextbullet\ }%
    \hangindent=\boxwid%
    \oldtextbullet}
    
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Tony Shen}{
    % xxx-xxx-xxxx -> Phone Number
	\normalfont +1 (778) 681-9007 
	\textbullet{}\normalfont \href{https://github.com/tsa87}{ github.com/tsa87} 
	\textbullet{}\href{mailto:tonyzshen@gmail.com}{ tonyzshen@gmail.com}
        % \textbullet{} Canadian Citizen
}
% 	\textbullet{} \href{https://tonyshen-step-2020.appspot.com/}{\textbf{tonyshen}-step-2020.appspot.com/} \\


\descript{}
\postsectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education}
\sep
\hrulefill
\postsectionsep

\subsection{Northeastern University / Broad Institute of MIT and Harvard \hfill \normalfont Boston, MA}
\position{Visiting researcher}{Feb 2025 - Present}
\textbullet{} \textbf{Research:} Foundation model for bio-molecular generation, and antibiotics discovery applications. \\ 
\textbullet{} \textbf{Supervisor:} Dr. Wengong Jin 
\sectionsep
\subsection{Simon Fraser University \hfill \normalfont Burnaby, BC}
\position{PhD in Computing Science}{May 2023 - Present}
\textbullet{} \textbf{Research:} Structure-based drug design with generative flow networks and flow matching models.  \\
\textbullet{} \textbf{Supervisor:} Dr. Martin Ester \\
% \textbullet{} \textbf{Collaborators:}  Dr. Woo Youn Kim (KAIST), Dr. Artem Cherkasov (UBC), Dr. Simon Olsson (Chalmers)
\sectionsep

\position{BSc Joint Major in Computing Science \& Molecular Biology and Biochemistry \normalfont (GPA: 3.97/4.33)}{Jan 2019 - May 2023}
\sectionsep


\section{Selected Publications} 
\sep
\hrulefill
\postsectionsep 

\textbullet{} \textbf{Tony Shen*}, Seonghwan Seo*, Ross Irwin, Kieran Didi, Simon Olsson, Woo Youn Kim, Martin Ester. Compositional Flows for 3D Molecule and Synthesis Pathway Co-design. \textbf{Under conference submission, ICLR GEM and AI4MAT workshop}, 2025.
\\
\postsectionsep
\textbullet{} Seonghwan Seo, Minsu Kim, \textbf{Tony Shen}, Martin Ester, Jinkyoo Park, Sungsoo Ahn, Woo Youn Kim. Generative Flows on Synthetic Pathway for Drug Design. \textbf{International Conference on Learning Representations (ICLR)}, 2025. \\
\postsectionsep

\textbullet{} \textbf{Tony Shen}, Seonghwan Seo, Grayson Lee, Mohit Pandey, Jason R Smith, Artem Cherkasov, Woo Youn Kim, Martin Ester. \textit{\textbf{TacoGFN}}: Target Conditioned GFlowNet for Structure-Based Drug Design. \textbf{Transactions on Machine Learning Research (TMLR)}, 2024. \\
% \& NeurIPS GenBio Workshop (Spotlight)
\postsectionsep


% \sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Work Experiences} 
\sep
\hrulefill
\postsectionsep 

\subsection{{Transcripta Bio} \hfill \normalfont Palo Alto, CA}
\position{Machine Learning Consultant (Part-Time)}{Sep 2023 - Dec 2024}
\textbullet{} Leading experiments on generative models for molecules with desired gene expression, resulting in the discovery of several novel molecules with better predicted bioactivity profile. \\
\textbullet{} Enabling company's first ML-based virtual screening pipeline with compound library standardization, characterization and featurization - which resulted in several wet-lab validated hits. 

\sectionsep

\subsection{{Recursion} \hfill \normalfont Salt Lake City, UT}
\position{Software Engineer (Part-Time)}{Sep - Dec 2022}
\position{Software Engineering Intern}{Jun - Sep 2022}
\textbullet{} Implemented gene search and enrichment analysis of biological pathways with \textbf{React} and Python using known biology databases to accelerate drug-target discovery workflow. Setup SLO alerts using \textbf{OpenTelemetry} and \textbf{Prometheus}.\\ 
\textbullet{} Built full-stack graph visualization and analysis app for millions of relationships between biological entities using \textbf{Dash}. \\
\sectionsep

\subsection{{Amgen} \hfill \normalfont Burnaby, BC}
\position{Bioinformatics Co-op}{Jan - Apr 2022}
\textbullet{} Developed binding affinity prediction model of antibody and target protein on cell sorting data using \textbf{PyTorch} and ESM. \\
% , using \textbf{PyTorch} and ESM embedding. \\
% \textbullet{} Enabled \textbf{high-throughput virtual screening} by generating millions of mutational sequences and filtering for high binding affinity using ML model's prediction. Discovered potentially better binding candidate for antibody therapy program. \\
\textbullet{} Built Dash web app to visualize immune repertoire containing thousands of sequences through network graph. \\ 
% \textbullet{} Optimized the \textbf{NGS} sample preparation protocol (RT-PCR with UMI) for immune repertoire mining of XenoMouse. \\
\sectionsep

\subsection{{Google} \hfill \normalfont Waterloo, ON}
\position{Software Developer Intern}{May - Aug 2021}
\textbullet{} Introduced contrastive learning to Retail AI ranking model and reduced average first click position by 0.36 using \textbf{TensorFlow}. \\
\textbullet{} Implemented adaptive multi-objective loss balancing algorithms (GradNorm, Uncertainty Weighting) to reduce over-fitting in multi-task ranking model. \\
\textbullet{} Used \textbf{C++} and \textbf{Flume (Apache Beam)} to build metric aggregation pipelines that processed terabytes of search logs to provide insights on search quality. 
\sectionsep

\subsection{{Georgian} \hfill \normalfont Toronto, ON}
\position{Machine Learning Engineering Intern}{Sep - Dec 2020}
\textbullet{} Built \href{https://github.com/georgianpartners/hydra}{\textbf{ML Platform}} command line tool that enables data scientists to seamlessly train hundreds of \textbf{docker}ized reproducible experiments on cloud in one command.  \\
\textbullet{} Trained and evaluated models predicting startups' raise likelihood to help investment team on candidates prioritization. \\ % for the multi-billion growth-stage tech venture capital. \\
\textbullet{} Generated novel features from large news dataset using \textbf{Apache Spark} and \textbf{increased AUPR by 10\%} compared to baseline.\\
% \textbullet{} Create repeatable \textbf{Google Cloud} infrastructure setup using \textbf{Terraform} \\
\sectionsep

\subsection{{Google} \hfill \normalfont Waterloo, ON}
\position{STEP Intern}{May - Aug 2020}
\textbullet{ Proposed and implemented a \href{https://github.com/googleinterns/step81-2020}{full stack web \& mobile platform} that enables non-technical users to create functional bots.} \\
\textbullet{ Owned and developed \textbf{Flutter/Dart} application and \textbf{Cloud Firestore} component. Proposed and communicated key technical designs in schema and framework choice, resulting in accelerated completion of cross-platform app. } \\
\textbullet{} 20\% Project: Worked with Cloud Health team to generate human mutation histogram, using \textbf{SQL} and \textbf{Python} to pull data from Genome Aggregation Database in \textbf{BigQuery}.
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROFESSIONAL EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 





%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Leadership and Honors
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \textbullet{} Grayson Lee, \textbf{Tony Shen}, Martin Ester. Geometric-informed GFlowNets for Structure-Based Drug Design. \textbf{Molecular Machine Learning Conference (MoML) Spotlight}, 2024. \\
% \postsectionsep

% \textbullet{} Atia Hamidizadeh, \textbf{Tony Shen}, Martin Ester. Semi-Supervised Junction Tree Variational Autoencoder for Molecular Property Prediction. \textbf{AAAI Deep Learning on Graphs Workshop}, 2023.
%[{ \href{https://github.com/tsa87/semi-jtvae}{code} /  \href{https://arxiv.org/abs/2208.05119}{\textbf{paper}}}].

% \position{AAAI'23 Deep Learning on Graphs Workshop}{Feb 2023}
% \textbullet{ Topic: Semi-Supervised Junction Tree Variational Autoencoder for Molecular Property Prediction}
\postsectionsep  



\section{Technical Skills} 
\sep
\hrulefill
\postsectionsep

\textbf{Programming Languages:} Python, C/C++, Java, JavaScript, SQL. \\
\postsectionsep
\textbf{Technical Tools:} PyTorch, Tensorflow, Spark, Beam, Flutter, React, Dash, PyMol, RDKit, Docker, Google Cloud, AWS. \\
\postsectionsep
\textbf{Research Interest:} AI for Drug Discovery, Generative Models, Flow Matching, Diffusion Models, Geometric Deep Learning, GFlowNets.


\sectionsep

\section{Communications} 
\sep
\hrulefill
\postsectionsep

\subsection{Guest interviewer - InterBios Podcast \hfill \normalfont May 2024}
Interviewed Dr. Anthony Fejes - CEO of HTuO Biosciences on the role of molecular simulation on drug discovery. 

\sectionsep

\subsection{Guest writer - Valence Portal Blogs \hfill \normalfont Apr 2024}
Published article on AI for Drug Design and Generative Flow Networks (\href{https://portal.valencelabs.com/blogs/post/mle-is-not-all-you-need-for-structure-based-drug-design-N2BmutTw8mMj34K}{link})
\sectionsep

\section{Supervising} 
\sep
\hrulefill
\postsectionsep

\subsection{Grayson Lee \hfill \normalfont Oct 2023 - May 2024}
Geometric-informed GFlowNets for Structure-Based Drug Design - \textbf{MoML 2024 (Spotlight)}
\sectionsep

\section{Academic Service} 
\sep
\hrulefill
\postsectionsep

\subsection{Reviewer}
\position{Transactions on Machine Learning Research (TMLR)}{Oct 2024 - }

\sectionsep

\section{Project Experiences} 
\sep
\hrulefill
\postsectionsep

\subsection{SFU Community Trust \hfill}
\position{Summer Intern / Project Founder}{May - Aug 2019}
\textbullet{} Created a pilot for co-living residence by converting existing units and provided affordable housing to 8 students.\\
\textbullet{} Presented feasibility report to developers and Campus Planning Director, resulting in elevated interest for coliving concepts.
\sectionsep

\subsection{InHouse Mobile \hfill}
\position{Founder}{Jan - May 2020}
\textbullet{Developed mobile ordering platform for restaurants during COVID-19 - using \textbf{React Native/Java Script}, \textbf{Expo} and \textbf{MongoDB}, and delivered both customer facing and restaurant-end apps with-in 3 months.} \\
\textbullet{ Led a 4-student team and improved development process through weekly code sprints, code reviews and bi-weekly standups.} \\
\sectionsep

% \subsection{SFU Unmanned Aerial Vehicle \hfill \normalfont S\lowercase{urrey}, BC}
% \position{Machine Vision Lead (Gesture Control Project)}{Oct 2018 - Sep 2019}
% \textbullet{} Built a vision-based hand movement tracking system 
% using \textbf{OpenCV} and \textbf{Tensorflow Object Detection API}.\\
% \textbullet{} Devised heuristic to determine hand movement from frame to frame predictions using \textbf{Python}.
% \sectionsep


\section{Awards}
\sep
\hrulefill
\postsectionsep

\subsection{Undergraduate Open Scholarship \hfill \normalfont 2020 - 2023}
Semester GPA above 4.0 (equivalent to A) in 2020 Spring, 2020 Fall, 2021 Spring, 2021 Fall, 2022 Fall and 2023 Spring.
\postsectionsep

\subsection{HackSeqRNA 2020 - 1st Place \hfill \normalfont May 2020}
\textbullet{} Created, trained and evaluated 1-D Convolutional models on RNA targets to predict ASO effectiveness with \textbf{Keras}.\\
\postsectionsep  

\subsection{SFU Waste Sorting Robot Competition - 2nd Place \hfill \normalfont Mar 2019}
\postsectionsep 

\subsection{VANTEC Angle Investor Network Pitch Night - 2nd place \hfill \normalfont  Nov 2018}
\textbullet{} Pitched coliving student housing project and won 2nd place out of 7 upcoming startups.
\postsectionsep  

\sectionsep

% \section{Other Skills} 
% \sep
% \hrulefill
% \postsectionsep

% \textbf{Languages:} Mandarin (Native), French (Beginner) \\ 
% \textbf{Interests:} Running, Hiking, Yoga, Fencing. 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%	
\end{document}  \documentclass[]{article}

